\documentclass[10pt]{aqresume}
\usepackage{ragged2e}
\begin{document}
  \RaggedRight
  %\emergencystretch 2em

  \name{Augusto Sales de Queiroz}

  \position{Software Engineer}

  \tagline{\textbf{Back-end} software engineer with \textbf{front-end} experience, passionate about \textbf{writing code} to leverage the power of \textbf{data}.}

  \contact{+1 (425) 209-6729}{asqueiroz@outlook.com}{www.augustoqueiroz.com}{augustoqueiroz}{augustoqueiroz}

  \section{Experience}
    \cvsubsection{Microsoft}{Software Engineer}{Jan. \rq 23--Present}{
      \item \textbf{Fully designed} and \textbf{developed} an \textbf{API} to automatically \textbf{generate descriptions} for properties being listed through \textbf{Bing}. Leveraged user-provided structured information and \textit{OpenAI's GPT-3}, and deployed as an \textit{Azure Function}.
      \item \textbf{Trained} and \textbf{deployed} a \textbf{price estimation model} to suggest listing prices to homeowners listing with \textbf{Bing}. Used \textit{Python}, \textit{Sklearn}, \textit{ADF}, and \textit{Azure Functions}.
      \item Upgraded \textbf{fraud detection} system to \textbf{improve coverage} and \textbf{precision} by moving from a heuristic-based to an incremental penalty model and identify additional signals, including estimated price and user information and behavior.
    }

    \cvsubsection{Microsoft}{Software Engineer Intern}{May \rq 21--Aug. \rq 21}{
      \item \textbf{Designed} and \textbf{implemented entity clustering} for the Bing Real Estate answer on \textbf{maps}, clustering \textbf{millions} of real estate entities in the backend and creating a custom UX treatment for the cluster POIs. Leveraged \textit{Sklearn's KMeans} and \textit{Python's multiprocessing} for clustering and wrote custom logic in the \textit{TypeScript} UX codebase for the new treatment.
    }

    \cvsubsection{Gemu}{Software Engineer Contractor}{Mar. \rq 21--May \rq 21}{
      \item Co-\textbf{designed} and \textbf{implemented} a product to allow gamers to participate in \textbf{public user-created challenges} for \textbf{Brawl Stars} in the Gemu platform and track progress via integration with the game's public API. Used \textit{Node.js}, \textit{AWS Lambda}, and \textit{AWS Dynamodb}.
    }

    \cvsubsection{Inria}{Research Intern}{Mar. \rq 20--Dec. \rq 20}{
      \item \textbf{Designed} and \textbf{developed} an \textbf{experimentation suite} to test and validate a \textbf{novel bioinformatics tool}, automating its execution with different parameter sets and processing the results. Used \textit{Python}, \textit{Multiprocessing}, and \textit{Matplotlib}.
    }

  \section{Education}
    \cvsubsection{BSc. Computer Engineering}{Universidade Federal de Pernambuco}{2022}

    \cvsubsection{Computer Science Exchange Student}{Polytech Nice--Sophia}{2019--2020}

  \section{Skills}
    \vspace*{-1\multicolsep}
    \begin{multicols*}{3}
      []
      \raggedright\textbf{Programming}\\
      \textit{4+ years} Python / SQL\newline
      \textit{2+ years} C\# / C/C++ / Swift / JavaScript\newline
      \textit{others} Go
      \vfill\null
      \columnbreak

      \textbf{Technical}\\
      Git / Machine Learning / Azure / AWS / Data Engineering / Unit Testing / Embedded Systems Design \& Development / Linux / React
      \vfill\null
      \columnbreak

      \textbf{Languages}\\
      Portuguese (\textit{Native})\newline
      English (\textit{Fluent})\newline
      French (\textit{Advanced})
    \end{multicols*}
\end{document}
